Rotations and Insecticide Resistance initial plots

### 2017-11-20 inst/documents/rotations_notes.Rmd
notes

@@

~ fix migration rate to be between 0 & 1, where 1 is random movement.

~ time to 50% resistance.

~ improve plot legend to show when insecticide in use

@@

@@

>>>>

done ~ fix migration rate to be between 0 & 1, where 1 is random movement.

~ allowed plots not to show refuge

#high cost, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )

done ~ improve plot legend to show when insecticide in use

*20/11/17*

~ looking at refactoring the migration code in run_rot()

Can do this to get the allele frequencies for generation 2 (by )

RAF[,,,2]

~ currently it does 4 very similar calcs for m|f, refuge|active.

~ i can replace with single, except need to be acreful not to change values before they have been used in the other calculations.

FROM :
    for(temp_int in 1:n_insecticides){

   }

TO :

    mig_intervention <- (1-migration_rate_intervention)*RAF[,, 'intervention', gen]+
                           migration_rate_intervention *RAF[,, 'refugia', gen]

    mig_refugia      <- (1-migration_rate_refugia)*RAF[,, 'refugia', gen]+
                           migration_rate_refugia *RAF[,, 'intervention', gen]

    RAF[,, 'intervention', gen] <- mig_intervention
    RAF[,, 'refugia', gen] <- mig_refugia

# testing multiplying RAF arrays
# to allow making code more concise

RAF <- set_start_freqs(n=3, max_generations = 1, freqs=c(0.1,0.01,0.001))
RAF2 <- set_start_freqs(n=3, max_generations = 1, freqs=c(1,2,3))

RAF * RAF2
           sex
insecticide     m     f
          1 0.100 0.100
          2 0.020 0.020
          3 0.003 0.003

@@

~ put migration code into a function and add a test

@@

~ time under resitance threshold, e.g. 50%

* rotations understand code better
* rotations add catch to stop freq declining
* rotate when resistant add catch to stop switch back to insecticide used < x years ago

@@

~ RAF[,,,2] to get allele frequencies for generation 2 (by insecticide,sex and active|refuge)
